Chimera Model Problems and Solution Schemes

### 2012-08-06 doc/model_problems/model_problems.tex
model problem updates

%%---------------------------------------------------------------------------%%
\section{Introduction}
In this document, finite volume formulations for the 2D incompressible
Navier-Stokes equations and conduction equation are generated. The
computational grid, boundary conditions, time integrations, and
solution methods are also formulated. Using these formulations, the
conjugate heat transfer problem is posed. These model problems and
solution schemes will be used within the Chimera code framework.

%%---------------------------------------------------------------------------%%
\section{Computational Grid}

@@

%%---------------------------------------------------------------------------%%
\section{Incompressible Navier-Stokes Equations}

>>>>

%%---------------------------------------------------------------------------%%
\section{Introduction}
In this document, finite volume formulations for the 2D incompressible
Navier-Stokes equations and conduction equation are generated using an
Eulerian approach. The computational grid, boundary conditions, time
integrations, and solution methods are also formulated. Using these
formulations, the conjugate heat transfer problem is posed. These
model problems and solution schemes will be used within the Chimera
code framework to demonstrate nonlinear capabilities.

%%---------------------------------------------------------------------------%%
\section{Computational Domain}

@@

%%---------------------------------------------------------------------------%%
\section{Incompressible Navier-Stokes Equations}
The incompressible Navier-Stokes equations describe a fluid a constant
density. The will generated through mass, momentum, and energy
conservation statements with an equation of state to close the system.

\subsection{Mass}

\subsection{Momentum}

\subsection{Energy}
For energy conservation, we choose a temperature framework in the same
manner as the conduction problem.

\subsection{Equation of State}
